\chapter{Problem 1}
\label{chp:intro}
\section{User Story}
\subsection{Heat food}
Cory Vince has just come home from a long day at the office, and he is very hungry. However, Cory doesn’t just eat anything, so he finds a TV-Dinner, because it only need a few minutes in the microwave. So he opens his microwave to put his dinner in, and then he specifies the required time using the buttons. After that he specifies the intensity for which the meal is supposed to be cooked, and presses start. Cory can hang his coat and do laundry in the meantime, because an audible signal will notify him about the completion of his meal.

When the signal has alerted Cory, he may open the door to the microwave and take his warm and cooked meal. If Cory had wanted to, he could have opened the door before the signal, and taken his food. In this case the food would have had less time to get warm. After the signal has been played, the microwave is immediately ready for next use, as long as the meal is changed if necessary.

\section{Functional requirements}

\begin{enumerate}[label=FR-\arabic*:]

\item The user must be able to use intensity for the cooking
\item The microwave must have a cooking timer where the user can indicate desired cooking time
\item When the timer runs out the microwave must turn off
\item When the timer runs out a buzzer must notify the user
\item The microwave must automatically turn off if the door is open
\item A door switch must indicate whether the door of the microwave is closed
\item When the start button is pushed the microwave must start

\end{enumerate}

\section{Non-functional requirements}

\begin{enumerate}[label=NFR-\arabic*:]
 \item Measures: 0.43 cm (w) * 39 cm (d) * 35 (h) approx.
 \item Casing: polished steel ($\approx$ 1.5 mm)
 \item Power supply: 230 V AC
\end{enumerate}
